\documentclass[a4paper,10pt]{article}
\thispagestyle{empty}

\usepackage[utf8]{inputenc}
\usepackage[cm]{fullpage}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{marvosym}

\newcommand{\name}[1]{\textbf{\huge{#1}}}
\newcommand{\header}[1]
{
\vspace{0.40in}
{\Large \textbf {\uppercase{#1}}}
\vspace{0.05in}
\hrule
\vspace{0.15in}
}
\newcommand{\spacer}{\vspace*{1\baselineskip}}

\newenvironment{details}
{\begin{itemize}[label=\scalebox{.5}{\ding{117}},leftmargin=0.15in]}
{\end{itemize}}

\begin{document}

\name{LYLE FRANKLIN}\\
\indent
LyleJFranklin@gmail.com | 765.993.5947

% first column
\begin{minipage}[t]{0.5\textwidth}
\header{Experience}


\textbf{IBM\\Extreme Blue Intern}\\
Austin, TX\\
May '14 - Aug. '14

\begin{details}
  \item One of only 32 hires out of 1,800 applicants (\textless2\% acceptance rate)
  \item Built system to allow non-technical users to deploy solutions to IBM's Bluemix cloud hosting service
  \item Utilized Vagrant, Docker, and Cloud Foundry to standardize development and production environments
  \item Pitched project to executives and distinguished engineers on a weekly basis 
\end{details}

\textbf{INTERACTIVE INTELLIGENCE\\Application Developer}\\
Indianapolis, IN\\
Dec. '12 - July '13

\begin{details}
  \item Designed and implemented internal business tools used by hundreds of employees
  \item Used rapid prototyping, quickly implemented new features and bug fixes based on user feedback
  \item Full-stack development: Implemented database, server-side REST API, front-end JS frameworks, and CSS
\end{details}


\textbf{UNIVERSITY OF ILLINOIS\\Undergraduate Researcher Intern}\\
Urbana-Champaign, IL\\
May '12 - Aug. '12

\begin{details}
  \item Developed refactoring plugin for the NetBeans IDE
  \item Plugin accepted as official patch to NetBeans’ source code
  \item Paper accepted at European Software Engineering Conference '13
\end{details}

\textbf{VIRGINIA B. BALL CENTER\\Technical Lead}\\
Muncie, IN\\
Jan. ‘12 - May ‘12

\begin{details}
  \item Collaborated with an interdisciplinary team of students to create
an online game for the Indianapolis Children’s Museum
  \item Student-driven studio learning, worked from 8 to 5 Monday
through Friday for a full semester
  \item Developed game with Unity3D, participated in daily Scrum meetings, and utilized Test-driven
development
\end{details}

\end{minipage}
\hspace{0.35 in}
% column 2
\begin{minipage}[t]{0.35\textwidth}
\header{Education}

\textbf{Univ. of Southern California\\
M.S. in Computer Science\\}
Spec. in Software Engineering\\
Expected Graduation: Dec. '14\\
GPA: 4.00
\spacer

\textbf{Ball State Univ.\\
B.S. in Computer Science\\}
Minor in Foundations of Business\\
Graduated: Dec. '12\\
GPA: 3.95

\spacer

\header{Skills}

\textbf{Languages:}\\
Java, JavaScript, CSS/LESS/SASS, Python (learning)

\spacer

\textbf{Frameworks:}\\
Node.js, Backbone.js, AngularJS, Django, Twisted

\spacer

\textbf{Databases:}\\
MySQL, MongoDB

\spacer

\header{Toolbox}

\textbf{Build:}\\
Grunt, Vagrant, Docker, Bower

\spacer

\textbf{Test:}\\
Jenkins, Travis, Karma, Selenium

\spacer

\textbf{Deploy:}\\
IBM Bluemix, Cloud Foundry, EC2, Heroku

\spacer\spacer

\header{Interests:}
\begin{details}
  \item Building Developer Tools
  \item Scrum/Extreme Programming
  \item Automation
  \item Test-Driven Development
\end{details}

\end{minipage}

\end{document}
